# Communicable, Maternal, Neonatal, and Nutritional Disease Burden (CMNN)

```{r}
# Load necessary packages
pacman::p_load(tidyverse, knitr, here)

# Import the communicable diseases data
data_cmnn <- read_csv(here("data/burden-of-disease-cmnn.csv"))
```
```{r include=FALSE}
unique(data_cmnn$Entity)
```



```{r}
# Filter the dataset to include only the three countries chosen by your group.
data_cmnn_mini <- data_cmnn %>% 
  filter(Entity %in% c("Guinea", "Switzerland", "Ethiopia"))
```

## Table of Estimates for CMNN Burden Over Time

```{r}
# Here render a table for the DALY burden over time for the three countries.
# You should pivot the data wider to show each country in a separate column.
data_cmnn_wide <- data_cmnn_mini %>% 
  select(!Code) %>% 
  pivot_wider(names_from = Entity, values_from = 3)
data_cmnn_wide
# Use kable() from the knitr package to render the table.
```

## Plot Showing Trends in CMNN Burden Over Time

```{r}
data_cmnn_mini2 <- data_cmnn_mini %>% 
  rename(DAILY = "DALYs (Disability-Adjusted Life Years) - Communicable, maternal, neonatal, and nutritional diseases - Sex: Both - Age: Age-standardized (Rate)")
```


```{r}
# Here, plot a line graph showing the trend of DALY burden for the chosen countries over time. You can use ggplot2 to create this plot. Each country's line should be a different color.
# NOTE: Use your long 'mini' data frame for plotting, not the wide data used for the table.
Plot_trend <- ggplot(data_cmnn_mini2, mapping = aes(x =Year,
                                                    y = DAILY,
                                                    color = Entity)) +
  geom_line()

Plot_trend

```

## Summary of CMNN Burden Findings

Provide a brief analysis based on the data presented in the table and chart. Highlight any significant findings or patterns. About 3 sentences.

## Attribution

This section was completed by Bapaté BARRY

The link to the group's GitHub repository is [WRITE THE LINK HERE!]
