# Non-Communicable Disease Burden (NCD)

```{r}
# Load necessary packages
pacman::p_load(tidyverse, knitr, here, kableExtra)

# Import the non-communicable diseases data
data_ncd <- read_csv(here("data/burden-of-disease-ncd.csv"))
```

```{r}
# Filter the dataset to include only the three countries chosen by your group.
countries <- c("Guinea", "Ethiopia", "Switzerland")

data_ncd_mini <- data_ncd %>% 
  filter(Entity %in% countries) %>% 
  rename(DALYs = `DALYs (Disability-Adjusted Life Years) - Non-communicable diseases - Sex: Both - Age: Age-standardized (Rate)`)

```

## Table of Estimates for NCD Burden Over Time

```{r}
# Here render a table for the DALY burden over time for the three countries.
# You should pivot the data wider to show each country in a separate column.
data_ncd_wide <- data_ncd_mini %>% 
  select(., -Code) %>% 
  pivot_wider(names_from = Entity, values_from = DALYs)

data_ncd_wide %>% 
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover"))


# Use kable() from the knitr package to render the table.
```

## Plot Showing Trends in NCD Burden Over Time

```{r}
# Here, plot a line graph showing the trend of DALY burden for the chosen countries over time. You can use ggplot2 to create this plot. Each country's line should be a different color.
# NOTE: Use your long 'mini' data frame for plotting, not the wide data used for the table.


data_ncd_mini %>% 
  ggplot(aes(x=Year, y=DALYs, color=Entity)) +
  geom_line() +
  labs(y = "DALYs lost", color = "Country")+
  scale_color_manual(values=c("#CC6666", "#9999CC", "#66CC99"))
  


```

## Summary of NCD Burden Findings

In Ethiopia, the NCD burden (total DALYs lost) decreased significantly since the 90s.
In Switzerland, a decrease was also reported but in a smaller scale.
In Guinea, the NCD burden is stable since the 90s but a small decrease was identifed in the late 2010's. To be confirmed with updated data. 


## Attribution

This section was completed by Anaïs Léger

The link to the group's GitHub repository is https://github.com/bapatbarry87-ops/rmc_week_02_workshop_BBAI
