# Overall Disease Burden

```{r}
# Load necessary packages
pacman::p_load(tidyverse, knitr, here)

# Import the overall disease data
data_overall <- read_csv(here("data/burden-of-disease-all-causes.csv"))

#guinea, switzerland, ethiopia
```

```{r}
# Filter the dataset to include only the three countries chosen by your group.
data_overall_mini <- data_overall%>%
  filter(Entity %in% c("Ethiopia", "Switzerland", "Guinea"))

data_overall_mini <- data_overall_mini%>%
  rename("Dalys" = `DALYs (Disability-Adjusted Life Years) - All causes - Sex: Both - Age: Age-standardized (Rate)`)

```

## Table of Estimates for Overall Disease Burden Over Time

```{r}
# Here render a table for the DALY burden over time for the three countries.
# You should pivot the data wider to show each country in a separate column
# Use kable() from the knitr package to render the table.

data_overall_wide <- data_overall_mini%>%
  select(-Code)%>%
  pivot_wider(
    names_from = "Entity", 
    values_from = "Dalys"
  )

knitr::kable(data_overall_wide)
```

## Plot Showing Trends in Overall Disease Burden Over Time

```{r}
# Here, plot a line graph showing the trend of DALY burden for the chosen countries over time. You can use ggplot2 to create this plot. Each country's line should be a different color.
# NOTE: Use your long 'mini' data frame for plotting, not the wide data used for the table.



plot_trend <- ggplot(data = data_overall_mini, mapping = aes(
  x = Year, y = Dalys, color = Entity))+
  geom_line()

print(plot_trend)





```

## Summary of Overall Disease Burden Findings

Provide a brief analysis based on the data presented in the table and chart. Highlight any significant findings or patterns. About 3 sentences.

## Attribution

This section was completed by Yabi B. 

The link to the group's GitHub repository is https://github.com/bapatbarry87-ops/rmc_week_02_workshop_BBAI
